\documentclass[11pt,a4paper]{article}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage{amsmath,amsfonts,amssymb}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage[margin=1in]{geometry}
\usepackage{cite}

\title{\textbf{Scalable Second-Order and Hybrid Methods for Optimization with Discontinuous Regularizations}\\
\large FAPESP BEPE Research Proposal}

\author{
    \textbf{Candidate:} Gabriel Belém Barbosa \\
    \textbf{Home Advisor:} Prof. Dr. Paulo José da Silva e Silva (UNICAMP) \\
    \textbf{Host Supervisor:} Prof. Dr. Dominique Orban (Polytechnique Montréal)
}
\date{Proposed period: September 2026 -- August 2027}

\begin{document}

\maketitle

\begin{abstract}
This research project proposes a research internship abroad (BEPE) at Polytechnique Montréal under the supervision of Prof. Dominique Orban. The main objective is to develop scalable second-order and hybrid methods for large-scale optimization problems involving discontinuous regularizations, particularly cardinality constraints ($L_0$ norm) and group sparsity. The proposal bridges the highly efficient first-order heuristics (Nonmonotone Spectral Proximal Gradient - NSPG, coordinate descent, and local combinatorial algorithms) developed during the PhD in Brazil with the advanced nonsmooth optimization machinery, such as trust-region and cubic regularization methods, researched by the host group. Beyond theoretical and algorithmic development, the project envisions robust implementations within the open-source \texttt{JuliaSmoothOptimizers} (JSO) ecosystem, providing direct contributions to the optimization software community.
\end{abstract}

\tableofcontents
\newpage

\input{1_introducao_en}
\input{2_objetivos_en}
\input{3_metodologia_en}
\input{4_plano_trabalho_en}

\bibliographystyle{plain}
\bibliography{bibliografia}

\end{document}
